Missing the Point$\colon$ Non-Convergence in Iterative Imputation Procedures

### 2020-04-09 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Started working on convergence diagnostics for pca component. Only works for 1 simulation now.

Missing data problems are ubiquitous and pervasive. **or** Everybody who works with person data is likely to run into a missing data problem.  
<!-- At some point, any social scientist  -->
<!-- <!-- conducting statistical analyses  --> -->
<!-- will run into a missing data problem [@alli02].  -->
Missingness is problematic because statistical inference cannot be performed on the whole data without employing \emph{ad hoc} solutions (e.g., list-wise deletion), which may yield wildly invalid results [@buur18]. A popular method to obtain statistically valid results despite of missing data is 'multiple imputation' [MI; @rubin76]. The multiple imputation method can be roughly divided into 3 steps: First, each missing value in an incomplete dataset is 'imputed' (i.e., filled in) several times by some algorithmic procedure. Next, the analysis of scientific interest is performed on each of the completed datasets. And finally, the results of these analyses are pooled into a single aggregated statistic.

@@

**Add the function `mvtnorm::rmvnorm()` back in**

The complete data is 'amputed' once for each simulation repetition with function `mice::ampute(). (**change this:** The missingness is univariate, and the probability to be missing is the same for all four variables, namely 20\% (`prop = 0.8, mech = "MCAR"`). This leaves 20\% of the rows completely observed). **(Add different percentages missingness??)** This study only considers only an MCAR missingness mechanism. Therefore, results may not be extrapolated to other missing data problems. Proper performance of the convergence diagnostics under MCAR is necessary but not sufficient to demonstrate appropriateness of $\widehat{R}$ and $AC$ as convergence diagnostics. This is just a proof of concept.

Missing datapoints are imputed with the function `mice::mice()`. All MI procedures are performed with Bayesian linear regression imputation (`method = "norm"`), and five imputation chains (`m = 5`). The number of iterations varies between simulation conditions (`maxit = ` $$1, 2, \dots, 100$$).

What to evaluate?

- bias in regression coefficients

- bias in $R^2$ (= coefficient of determination)

-

@@

```{r, include = FALSE}
load("../Results/75percentmiss.Rdata")
source("../2.CreateFigures.R")
```

@@

```{r, echo = FALSE}
load("../Results/combined.Rdata")

>>>>

Missing data problems are ubiquitous and pervasive. **or** Everybody who works with person data is likely to run into a missing data problem.  
<!-- At some point, any social scientist  -->
<!-- conducting statistical analyses  --> <!-- will run into a missing data problem [@alli02].  -->
Missingness is problematic because statistical inference cannot be performed on the whole data without employing \emph{ad hoc} solutions (e.g., list-wise deletion), which may yield wildly invalid results [@buur18]. A popular method to obtain statistically valid results despite of missing data is 'multiple imputation' [MI; @rubin76]. The multiple imputation method can be roughly divided into 3 steps: First, each missing value in an incomplete dataset is 'imputed' (i.e., filled in) several times by some algorithmic procedure. Next, the analysis of scientific interest is performed on each of the completed datasets. And finally, the results of these analyses are pooled into a single aggregated statistic.

@@

**Add the function `mvtnorm::rmvnorm()` back in** use citation("mvtnorm")

The complete data is 'amputed' once for each simulation repetition with function `mice::ampute()`. (**change this:** The missingness is univariate, and the probability to be missing is the same for all four variables, namely 20\% (`prop = 0.8, mech = "MCAR"`). This leaves 20\% of the rows completely observed). **(Add different percentages missingness??)** This study only considers only an MCAR missingness mechanism. Therefore, results may not be extrapolated to other missing data problems. Proper performance of the convergence diagnostics under MCAR is necessary but not sufficient to demonstrate appropriateness of $\widehat{R}$ and $AC$ as convergence diagnostics. This is just a proof of concept.

Missing datapoints are imputed with the function `mice::mice()`. All MI procedures are performed with Bayesian linear regression imputation (`method = "norm"`), and five imputation chains (`m = 5`). The number of iterations varies between simulation conditions (`maxit = ` $1, 2, \dots, 100$).

<!-- What to evaluate? -->

<!-- - bias in regression coefficients -->

<!-- - bias in $R^2$ (= coefficient of determination) -->

<!-- -  -->

@@

```{r, include = FALSE}
load("../Results/combined.Rdata")
source("../2.CreateFigures.R")
```

@@

```{r, echo = FALSE}
#load("../Results/combined.Rdata")
